Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-21 paper/structureScene.tex
display definition of x_1

The wavelet transform $\boldsymbol{}$ of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelets:
$\boldsymbol{y_1}(t, \gamma_1) =
(\boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}})(t)$.
Applying pointwise complex modulus to $\boldsymbol{y_1}$ yields
the wavelet scalogram
$\boldsymbol{x_1}(t, \gamma_1) = \vert \boldsymbol{y_1}(t, \gamma_1)\vert$.
The wavelet scalogram bears resemblance with the constant-Q transform (CQT),
which is derived from the short-time Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q}$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the wavelet scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the CQT has a fixed temporal resolution, constrained by the support of the STFT analyzing window.
Therefore, the wavelet scalogram has a better temporal localization at high
frequencies, which allows to observe steady amplitude modulations.

>>>>

The wavelet transform $\boldsymbol{}$ of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelets:
$\boldsymbol{y_1}(t, \gamma_1) =
(\boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}})(t)$.
Applying pointwise complex modulus to $\boldsymbol{y_1}$ yields
the wavelet scalogram
\begin{equation}
\boldsymbol{x_1}(t, \gamma_1)
= \vert \boldsymbol{y_1}(t, \gamma_1)\vert
= \vert \boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}} \vert (t).
\end{equation}
The wavelet scalogram bears resemblance with the constant-Q transform (CQT),
which is derived from the short-time Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q}$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the wavelet scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the CQT has a fixed temporal resolution, constrained by the support of the STFT analyzing window.
Therefore, the wavelet scalogram has a better temporal localization at high
frequencies, which allows to observe steady amplitude modulations.
